A deeper look into bug fixes: patterns, replacements, deletions, and additions

### 2016-02-17 MSRChallenge2016.tex
RElocating related work
Several changes
MSR paper
Mauricio Soto   9:02 PM
To: clegoues@cs.cmu.edu, chupanw@cs.cmu.edu, fthung@andrew.cmu.edu,
Mauricio Soto

- I changed the references to bibtex.
- I rewrote the intro to make it more high level
- I relocated the Related Work to be section 2, because that's what we
talked in the meeting, though I'm not super convinced it is working for
us over there.
- I removed my Append/Delete query section because that is not actually
the one that we ran. We ran Pan's. Pan: Maybe you can put something in
the methodology regarding the query you ran and your re

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Mauricio Soto\\
       \affaddr{School of Computer Science}\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{mauriciosoto@cmu.edu}
       % 3rd. author
\alignauthor Ferdian Thung\\
       \affaddr{University}\\
       \affaddr{City}\\
       \email{email@domain.com}
% 2nd. author
\alignauthor Chu Pan Wong   \\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{email@domain.com}       
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor
Claire Le Goues\\
       \affaddr{School of Computer Science}\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{clegoues@cs.cmu.edu}
% 5th. author
\alignauthor
David Lo\\
       \affaddr{University}\\
       \affaddr{City}\\
       \email{author@edu}       
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{February 2, 2016}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
\textbf{
With the rise of automated program repair in the last couple of years, there are a lot of questions to remain unanswered. We performed a study on the Github dump of September 2015 in which we analyzed all the fixing revisions of this dataset, and found all the replacements made in these 46,301,429 files from real life projects in Github.
}

\textbf{
We found very valuable information to guide automatic software repair, such as the most common and least common replacements made by human developers in order to build a successful patch; we analyzed the most and least common statement to replace others, and the most and least likely statement to get replaced by other. We also analyzed, once you have a statement that you want to replace (a faulty statement), what are the most likely statements to replace it for. These information will help automatic program repair tools to be more maintainable and user friendly, taking it one step closer to what humans developers do to repair their code.
}

@@

Automatic bug repair is the branch of computer science that deals with automated
ways to repair errors in software. There have been several approaches taken
towards improving the different methodologies to repair bugs in software
automatically~\cite{kim2013,weimer2009,legoues2012,pan2009}, one of the
most accepted approaches so far has been GenProg~\cite{weimer2009,legoues2012}, an
evolutionary program repair tool which applies four different kinds of possible
edits to code in order to find a patch for a given bug. These changes are the
following: Delete, Replace, Swap and Append.

\todo{We need to integrate the PAR and operator discussion a bit better.  Let's
  take it up a level of abstraction: there is initial work in applying these
  techniques to Java that propose a number of mutation operators, and we study
  the degree to which they apply in practice and make recommendations based on
  human-provided repairs.  Doing so is a good idea, because patches inspired by
  human-created repairs are empirically demonstrated to be rated more highly by
  developers (cite PAR).}
\todo{I also thought we were doing Par first, and then the replacement studies?}

Another well known approach is PAR~\cite{kim2013}, which creates 10 different
repair templates and applies them to the buggy code in an effort to repair
it. In this paper we have taken 7 out of the 10 PAR templates and tested how
common they are in the repairs made by programmers in the latest official data
dump of Github as of September 2015 provided by~\cite{dyer2013}.

Our research aims to provide guidelines to improve three out of four of these
possible changes: Delete, Replace and Append. It will provide the data necessary
for this tool and other approaches to have a guide on what is the way in which
human programmers change their code when coding a fix for a bug. This way it
will make it more likely for automatic error repair approaches to succeed in
finding a patch for a particular error, and also, to provide automatic error
repair software with heuristics to make the patches more human-like and
therefore more readable and maintainable by human developers.

In this article we study the frequency with which human programmers replace,
delete and append different statements to their source code in order to fix a
bug.

@@

\begin{table*}
	\centering
	\caption{Amount of appearances per replace kind}
	\resizebox{\textwidth}{100pt}{
		\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|} \hline
			&Assert&Break&Continue&Do& For&If&Label&Return&Case&Switch& Synchronized&Throw&Try&TypeDecl&While
			\\ \hline
			\texttt{Assert}	&-&340&	232	&27	&517	&1764&	14&	1260	&211	&191&	82&	1004	&352	&0	&206
			\\ \hline
			\texttt{Break} &455	&-&	1254&	176	&3757	&9096&	90&	10538&	771	&455&	672	&3123&	3660&	18&	2278
			\\ \hline
			\texttt{Continue} & 229	&1384	&-&	221	&1909	&3094&	85&	3486	&772&	635	&233&	1227&	1493&	30&	1086
			\\   \hline
			\texttt{Do} &32	&205&	171	&-&	474	&648	&12&	543	&106	&92&	44	&227	&325&	4&	558
			\\ \hline
			\texttt{For} &505	&3366	&1516	&316	&-&	14547	&56	&14924	&2791	&1852	&1044&	5642&	5796	&41	&6582
			\\ \hline
			\texttt{If}& 1402&	8820&	2430&	476	&13703&-&		247	&30489	&8639	&5710	&2472&	8960&	13714&	84&	5622
			\\ \hline
			\texttt{Label} &19&	44	&46	&6&	56	&255	&-&	270	&44	&22	&5	&80&	53&	2	&33
			\\ \hline
			\texttt{Return} &1219&	8603	&3009	&531	&12620	&28536&	164	&-&	6088&	3657&	2021&	15346&	11486&	71	&4684
			\\ \hline
			\texttt{Case} &298	&839&	506	&125&	3002&	8039&	33&	6261	&-&	126	&649&	2206&	2784&	24&	1864
			\\ \hline
			\texttt{Switch}&281	&533&	379	&56	&1997	&5175&	22	&4090&	126	&-&	212	&1571	&1311	&7&	878
			\\ \hline
			\texttt{Synchronized} &79&	606&	289&	66	&1122&	3070&	158&	2853	&562&	256	&-&	1303&	1274&	8	&466
			\\ \hline
			\texttt{Throw} &821&	2844&	1195	&197&	5993	&10664&	113&	16688&	2002	&1446&	936		&-&4443&	37&	1934
			\\ \hline
			\texttt{Try}& 440&	3976&	1254&	214	&6414&	16294&	45	&14119	&3178	&1509	&1243&	4795	&-&	46&	2218
			\\ \hline
			\texttt{TypeDecl} &2&	35&	15	&1&	49	&83&	1&	137	&21&	9&	4&	35&	46	&-&	11
			\\ \hline
			\texttt{While}& 301&	2295&	1016&	937	&8257&	6587&	41	&6280&	1866&	766	&606&	2028&	2677&	27	&-
			\\ \hline
		\end{tabular}
	}
\end{table*}

@@

\subsection{Replace Query}
The replace query is a query in which first we set the project that we are going
to use, which is the Github dump of September 2015 provided by~\cite{dyer2013}.

We then create a visitor to traverse all the nodes of this repository. First
thing the visitor does is to ask weather the node is a Revision, and if it is,
then it asks if it is a fixing revision. Therefore we are analyzing only files
that were already committed and are now being reviewed to fix an error. We use
Boa's infrastructure to do this by visiting the node they label as "Revision"
and then calling the function defined by Boa "isfixingrevision()".

A replacement needs two statements, one that is deleted and another one that is
inserted.  We then go through all the files that have been changed in this data
set asking for two conditions: it must be a fixing revision and there must have
been a previous version of this file before. If these conditions are met then we
initialize two counters: one for the first statement we are analyzing (the one
that was deleted), and another one for the second statement we are analyzing
(the one that was inserted).

At this point we visit each statement in the previous state of that changed
file, before the change was applied and we count the amount of appearances of
the first statement we are analyzing (the one that was deleted), and then we
count the amount of appearances of the second statement we are analyzing (the
one that was inserted). We save these values, and do the same for the latest
version of the file and save these values as well.

@@

We need to test this with all the possible combinations of two different
statement types since we want to know what is the probability of an specific
statement to be replaced by another specific statement. For example, we want to
know how often does a For loop gets replaced by a While loop in a successful
human written patch, or how often does a Break statement gets replaced by a
Continue statement in a successful human written patch.

Because of this we have created Table 1 which records the amount of replaces happening from one kind of statement to another. It is a matrix of fifteen by fifteen slots that describes which statements are being replaced by which other.

The numbers in the slots represent the amount of files in which that replacement took place. In the first column we have the list of statements that are being replaced, and on the top row we have the list of statements for which that statement was replaced for. For example, if we take the intersection of row 5 (DoStatement row) and column 2 (AsserStatement column), we have a 32, which means that from the 46,301,429 files categorized by Boa as fixing revisions in Github in the month of September 2015, only 32 of them replaced a DoStatement for an AssertStatement.

It is important to notice  that this analysis doesn't consider replacing an statement kind for a different version of the statement kind, since it is counting the amount of appearances of each statement kind. So, if for example, the developer modifies the condition inside of an if statement, the amount of if statements in the file is going to remain the same

\subsection{Delete/Append Query}
The Delete/Append Query is similar to the Replace Query with some variations to
count for the amount of times that a file was changed and a particular statement
kind was ei- ther deleted or append, and the rest of the statement kinds
remained the same.

We created a Boa file in which first we create an output variable to count all
the amount of files in which a statement kind was deleted or appended. Similar
to the previous query, we visit all the files labeled as fixing revisions, then
visit ev- ery node of the previous version of the revision, counting the amount
of statement kinds of each one of the possible fifteen different ones. We then
do the same for the later version of the revision, counting the different
statement kinds.

Finally, we compare the amounts of the previous version, with the new
version. For each of the revisions, we ask if the amount of statements stays the
same for all the statement kinds, except for X kind of statement. When the
amount of statements is different in the previous version than the latest
version for X kind of statement. Then we ask if X kinds of statement is greater
in the previous version or the latest ver- sion. If the amount of appearances of
X kind of statement is greater in the previous version than the latest version,
and all the remaining fourteen statement kinds have the same amount in the
previous than the latest version, then we say that one or more of the statements
of kind X were deleted. Otherwise, if the latest version has a greater amount of
ap- pearances of X kind of statement and the rest have the same amount of
appearances in both the previous and the latest version, then we say that one or
more statements of kind X were appended or added to the fixing revision.

@@

With this study, we are able to make a more accurate guess, when having a known faulty statement, to which statement it is more likely to replace it for. By performing simple math with the data of Table 1, we can find the most likely replacements that will end up being a successful patch.

@@

\includegraphics[scale=0.5]{g1.png}

@@

\includegraphics[scale=0.5]{g2.png}

\section{Related Work}
A similar study was performed by Dongsun Kim et al.~\cite{kim2013} in which they
look for the most common ways in which programmers patch bugs in software. The
researchers developed a variation of the tool Genprog~\cite{weimer2009,legoues2012}
with several different templates resembling patters programmers use to patch
bugs.

>>>>

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Mauricio Soto\\
       \affaddr{School of Computer Science}\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{mauriciosoto@cmu.edu}
       % 3rd. author
\alignauthor Ferdian Thung\\
       \affaddr{University}\\
       \affaddr{City}\\
       \email{email@domain.com}
% 2nd. author
\alignauthor Chu Pan Wong   \\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{email@domain.com}       
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor
Claire Le Goues\\
       \affaddr{School of Computer Science}\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA}\\
       \email{clegoues@cs.cmu.edu}
% 5th. author
\alignauthor
David Lo\\
       \affaddr{University}\\
       \affaddr{City}\\
       \email{author@institution.edu}       
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{February 2, 2016}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}

With the rise of automated program repair in the last couple of years, there are a lot of questions to remain unanswered. We performed a study on the Github dump of September 2015 in which we analyzed all the fixing revisions of this dataset, and found all the replacements made in these 46,301,429 files from real life projects in Github.

We found very valuable information to guide automatic software repair, such as the most common and least common replacements made by human developers in order to build a successful patch; we analyzed the most and least common statement to replace others, and the most and least likely statement to get replaced by other. We also analyzed, once you have a statement that you want to replace (a faulty statement), what are the most likely statements to replace it for. These information will help automatic program repair tools to be more maintainable and user friendly, taking it one step closer to what humans developers do to repair their code.

@@

Automatic bug repair is the branch of computer science that deals with automated
ways to repair errors in software. There have been several approaches taken
towards improving the different methodologies to repair bugs in software
automatically~\cite{kim2013,weimer2009,legoues2012,pan2009}. A well known approach is PAR~\cite{kim2013}, which creates 10 different repair templates and applies them to the buggy code in an effort to repair
it. In this paper we have taken 7 out of the 10 PAR templates and tested how
common they are in the repairs made by programmers in the latest official data
dump of Github as of September 2015 provided by~\cite{dyer2013}.

Some other well known approaches~\cite{weimer2009,legoues2012} have been based on the idea of applying a number of mutation operators to the buggy code in order to find a patch. In this opportunity, we study the degree to which these mutation operators apply in practice, taking as a subject of study several million human-made bug fixes from Github. This way it will make it more likely for automatic error repair approaches to succeed in
finding a patch for a particular error, and also, to provide automatic error
repair software with guidelines to make the patches more human-like and
therefore more readable and maintainable by human developers, as studied empirically by~\cite{kim2013}.

\section{Related Work}
We take as reference the study performed by Dongsun Kim et al.~\cite{kim2013} in which they look for the most common ways in which programmers patch bugs in software. The
researchers developed a variation of the tool Genprog~\cite{weimer2009,legoues2012}
with several different templates resembling patters programmers use to patch
bugs, and then perform an empirical study to evaluate which patches do human programmers prefer.

@@

@@

\begin{table*}
	\centering
	\resizebox{\textwidth}{100pt}{
		\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|} \hline
			&Assert&Break&Continue&Do& For&If&Label&Return&Case&Switch& Synchronized&Throw&Try&TypeDecl&While
			\\ \hline
			\texttt{Assert}	&-&340&	232	&27	&517	&1764&	14&	1260	&211	&191&	82&	1004	&352	&0	&206
			\\ \hline
			\texttt{Break} &455	&-&	1254&	176	&3757	&9096&	90&	10538&	771	&455&	672	&3123&	3660&	18&	2278
			\\ \hline
			\texttt{Continue} & 229	&1384	&-&	221	&1909	&3094&	85&	3486	&772&	635	&233&	1227&	1493&	30&	1086
			\\   \hline
			\texttt{Do} &32	&205&	171	&-&	474	&648	&12&	543	&106	&92&	44	&227	&325&	4&	558
			\\ \hline
			\texttt{For} &505	&3366	&1516	&316	&-&	14547	&56	&14924	&2791	&1852	&1044&	5642&	5796	&41	&6582
			\\ \hline
			\texttt{If}& 1402&	8820&	2430&	476	&13703&-&		247	&30489	&8639	&5710	&2472&	8960&	13714&	84&	5622
			\\ \hline
			\texttt{Label} &19&	44	&46	&6&	56	&255	&-&	270	&44	&22	&5	&80&	53&	2	&33
			\\ \hline
			\texttt{Return} &1219&	8603	&3009	&531	&12620	&28536&	164	&-&	6088&	3657&	2021&	15346&	11486&	71	&4684
			\\ \hline
			\texttt{Case} &298	&839&	506	&125&	3002&	8039&	33&	6261	&-&	126	&649&	2206&	2784&	24&	1864
			\\ \hline
			\texttt{Switch}&281	&533&	379	&56	&1997	&5175&	22	&4090&	126	&-&	212	&1571	&1311	&7&	878
			\\ \hline
			\texttt{Synchronized} &79&	606&	289&	66	&1122&	3070&	158&	2853	&562&	256	&-&	1303&	1274&	8	&466
			\\ \hline
			\texttt{Throw} &821&	2844&	1195	&197&	5993	&10664&	113&	16688&	2002	&1446&	936		&-&4443&	37&	1934
			\\ \hline
			\texttt{Try}& 440&	3976&	1254&	214	&6414&	16294&	45	&14119	&3178	&1509	&1243&	4795	&-&	46&	2218
			\\ \hline
			\texttt{TypeDecl} &2&	35&	15	&1&	49	&83&	1&	137	&21&	9&	4&	35&	46	&-&	11
			\\ \hline
			\texttt{While}& 301&	2295&	1016&	937	&8257&	6587&	41	&6280&	1866&	766	&606&	2028&	2677&	27	&-
			\\ \hline
		\end{tabular}
		}
		\caption{Amount of appearances per replace kind}
\end{table*}

\subsection{Replace Query}
The replace query we designed, is a query in which we create a visitor to traverse all the fixing revisions in this repository~\cite{dyer2013}. Therefore we are analyzing only files
that were already committed and are now being reviewed to fix an error.

We visit each statement in the previous state of that changed
file, before the change was applied and we count the amount of appearances of
the first statement we are analyzing (the one that was deleted), and then we
count the amount of appearances of the second statement we are analyzing (the
one that was inserted). We save these values, and do the same for the latest
version of the file and save these values as well.

@@

\todo{Note to self (Mau): Change this paragraph to explain the table depending on how it is presented}
The numbers in the slots represent the amount of files in which that replacement took place. In the first column we have the list of statements that are being replaced, and on the top row we have the list of statements for which that statement was replaced for. For example, if we take the intersection of row 5 (DoStatement row) and column 2 (AsserStatement column), we have a 32, which means that from the 46,301,429 files categorized by Boa as fixing revisions in Github in the month of September 2015, only 32 of them replaced a DoStatement for an AssertStatement.

It is important to notice  that this analysis doesn't consider replacing an statement kind for a different version of the same statement kind, since it is counting the amount of appearances of each statement kind. So, if for example, the developer modifies the condition inside of an if statement, the amount of if statements in the file will remain the same.

@@

\todo{Note to self (Mau): Change this depending on the table}
With this study, we are able to make a more accurate guess, when having a known faulty statement, to which statement it is more likely to replace it for. By performing simple math with the data of Table 1, we can find the most likely replacements that will end up being a successful patch.

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[scale=0.5]{g1.png}
  \caption{Most common replacements}
\end{figure}

@@

\begin{figure}
  \centering
\includegraphics[scale=0.5]{g2.png}
\caption{Least common replacements}
\end{figure}
